\documentclass[a4paper,9pt]{article}
\usepackage{latexsym}
\usepackage{microtype}
\usepackage[margin=0.55in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}

% ---------- Formatting ----------
\setlength{\parindent}{0pt}
\setlength{\parskip}{1pt}
\titleformat{\section}{\normalsize\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{6pt}{5pt}

\begin{document}
\linespread{1.05}

% =======================
% HEADER
% =======================
\begin{center}
    {\LARGE \textbf{Shubhu Rai}}\\[2pt]
    India \quad
    \href{https://github.com/shubhu121}{GitHub: shubhu121} \quad
    \href{https://www.linkedin.com/in/shubhu-rai-09340a367/}{LinkedIn: shubhu-rai}
\end{center}

% =======================
\section*{Summary}
Software Development Engineer and AI Engineer aspirant with strong experience in building scalable backend systems and intelligent applications. 
Proficient in C++, JavaScript, and Python with solid knowledge of Data Structures, Algorithms, Machine Learning, and system design. 
Experienced in developing AI-powered automation systems, APIs, and full-stack applications using Node.js and modern web technologies.

% =======================
\section*{Technical Skills}

\textbf{Languages:} C++, Python, JavaScript, C \\
\textbf{AI/ML:} Machine Learning, Random Forest, NLP, Prompt Engineering, LLM APIs \\
\textbf{Backend:} Node.js, Express.js, REST APIs \\
\textbf{Frontend:} HTML5, CSS3, React.js \\
\textbf{Databases:} MongoDB, MySQL \\
\textbf{Tools:} Git, GitHub, Playwright, Postman, VS Code \\
\textbf{Core CS:} Data Structures and Algorithms, OOP, DBMS, Operating Systems, System Design

% =======================
\section*{Projects}

\textbf{AI Code Assistant}
\hfill \textit{Python, LLM API, Node.js, React.js}
\begin{itemize}[leftmargin=12pt, itemsep=1pt]
\item Built an AI-powered coding assistant that generates explanations, optimizes code, and suggests fixes for bugs using \textbf{LLM APIs}.
\item Implemented code analysis pipeline supporting \textbf{C++, Python, and JavaScript}.
\item Designed an interactive interface allowing developers to upload code and receive structured suggestions and improvements.
\item Reduced debugging time by generating automated explanations and potential fixes for runtime and logical errors.
\end{itemize}

\vspace{3pt}

\textbf{Document Search Engine with Semantic Retrieval}
\hfill \textit{Python, NLP, Vector Embeddings, Node.js}
\begin{itemize}[leftmargin=12pt, itemsep=1pt]
\item Developed a semantic document search engine capable of retrieving contextually relevant information from large text datasets.
\item Implemented embedding-based similarity search using vector representations of documents.
\item Built REST APIs enabling efficient indexing and querying of documents.
\item Achieved faster search results and improved accuracy compared to traditional keyword-based search systems.
\end{itemize}

\vspace{3pt}

\textbf{Real-Time Chat Application with AI Moderation}
\hfill \textit{Node.js, WebSockets, MongoDB, AI Moderation API}
\begin{itemize}[leftmargin=12pt, itemsep=1pt]
\item Built a real-time messaging platform supporting instant communication using \textbf{WebSockets}.
\item Integrated AI-based content moderation to detect and filter abusive or inappropriate messages.
\item Implemented user authentication, chat rooms, and persistent message storage.
\item Optimized message broadcasting and server performance to support concurrent users efficiently.
\end{itemize}

\vspace{3pt}

\textbf{Smart Task Management System}
\hfill \textit{React.js, Node.js, MongoDB, Machine Learning}
\begin{itemize}[leftmargin=12pt, itemsep=1pt]
\item Developed a productivity platform that prioritizes tasks using a machine learning based ranking model.
\item Implemented predictive task scheduling based on user activity patterns.
\item Built REST APIs to manage tasks, deadlines, and notifications.
\item Designed a responsive UI for efficient task management and analytics visualization.
\end{itemize}
% =======================
\section*{Education}

\textbf{Bachelor of Technology in Computer Science} \\
Expected Graduation: 2026

% =======================
\section*{Achievements}

\begin{itemize}[leftmargin=12pt, itemsep=1pt]
\item Solved \textbf{1000+ Data Structures and Algorithms problems} across competitive programming platforms.
\item Built multiple automation and AI systems integrating \textbf{LLM APIs and intelligent agents}.
\item Strong problem-solving background using \textbf{C++ for algorithmic challenges}.
\end{itemize}

\end{document}